---
title: "P8105 Homework5"
author: "Xiangyi Liu (xl3048)"
date: "11/10/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 20, fig.height = 10
)

# knitr::opts_chunk$set(
#   fig.width = 6,
#   fig.asp = .6,
#   out.width = "90%"
# )
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data.

```{r, warning=FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r p2_df}
path_df = 
  tibble(
    path = list.files("./data/data"),
  ) %>%
  mutate(
    path = str_c("./data/data/",path),
    data = map(.x=path, ~ read.csv(.x)),
    file = list.files("./data/data")
  ) %>%
  select(-path) %>%
  relocate(file,data) %>%
  unnest(data) %>%
  separate(file,sep = "_", into = c("arm","ID")) %>%
  mutate(
    arm = case_when(
      arm == "con" ~ "control",
      arm == "exp" ~ "experimental"
    )
  ) %>%
  unite(arm_id,arm,ID,sep = "_")
path_df$arm_id<-gsub("\\..*","",path_df$arm_id)

write.csv(path_df,file = "./data/prob2_path_df.csv")

head(path_df)
```


```{r p2_plot}
path_longer_df<-path_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>%
  separate(arm_id,sep = "_",into = c("arm","id")) %>%
  unite(arm_id,arm,id,sep = "_",remove = F) %>%
  select(-id)


p<-ggplot(data = path_longer_df, aes(x = week, y = value, group = arm_id, color = arm))+
  geom_line()+
  theme(text = element_text(size=20))
p
```

At Week 1, two groups did not appear a significant difference. Only two participants from the experimental group had noteworthy higher measurements compared to the control group.\
During the course of the study, the difference between the two groups became gradually obvious. The measurements taken from the control group roughly remained at the same level from Week 1 to Week 8. However, the measurements taken from the experimental group increased steadily every week. At Week 8, all participants in the experimental group had a higher measurements than that of the control group. 

## Problem 3
```{r cache=TRUE}
set.seed(1)

trial_num = 5000
sim_mean_sd = function(samp_size=30, mu, sigma = 5) {

  sim_data = list(
    x=rnorm(n=samp_size, mean = mu, sd = sigma)
  ) %>% bind_rows()
  
}

sim_data <- rerun(trial_num,sim_mean_sd(mu=0))


result <- tibble(
  t_test = map(.x=sim_data,~t.test(.x))
 ) %>%
  mutate(
   tidy_tests = map(.x = t_test, ~broom::tidy(.x))
 ) %>%
select(-t_test) %>%
unnest(tidy_tests) %>%
select(estimate,p.value) %>%
rename(mu_hat = estimate)

head(result) %>% knitr::kable(digits = 3)

  
```


```{r cache=T}
mu_list = 
  list(
    "mu_0"  = 0,
    "mu_1"  = 1, 
    "mu_2"  = 2, 
    "mu_3" = 3, 
    "mu_4" = 4,
    "mu_5" = 5,
    "mu_6" = 6)


output_data = 
  tibble(mu_list = c(0,1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = mu_list, ~rerun(trial_num, sim_mean_sd(mu = .x)))
  ) %>%
  unnest(output_lists)

output_result<-tibble(
  t_test = map(.x=output_data$output_lists, ~t.test(.x,mu = 0))
) %>%
  mutate(
   tidy_tests = map(.x = t_test, ~broom::tidy(.x))
 )%>%
select(-t_test) %>%
unnest(tidy_tests) %>%
cbind(output_data$mu_list) %>%
rename(true_mu = `output_data$mu_list`) %>%
select(true_mu, estimate,p.value) %>%
relocate(true_mu, estimate,p.value)


```

```{r p3_plot}
reject_null_prop <- output_result %>%
  group_by(true_mu) %>%
  summarize(
    reject_null = sum(p.value<0.05)/n()
  ) %>%
  mutate(true_mu=as.factor(true_mu),
         fail_reject_null = 1-reject_null) 

plot_reject_null_prop <-reject_null_prop %>%
  pivot_longer(
    reject_null:fail_reject_null,
    names_to = "condition",
    values_to = "proportion"
  )

p1<-ggplot(data = plot_reject_null_prop, aes(fill = condition, y = proportion, x = true_mu))+
  geom_bar(position="stack", stat="identity")+labs(title = "Proportion of Times Reject The Null", x = "True Mu", y = "Proportion", fill = "Condition")+scale_fill_discrete(labels = c("Fail to reject H0", "Reject H0"))+
  theme(text = element_text(size=20))
p1

reject_null_prop%>% knitr::kable(digits = 3)
```
The effect size, d, is defined as the number of standard deviations between the null mean and the alternate mean, d = (μ1 - μ0)/σ \
\
μ0is the population mean for the null distribution, which is 0 in the case.\
\
We also know that the mean for alternative distributions (μ1) for each trial is 0, 1, 2,...,6 respectively. As mu1 increases, the difference between μ1 and μ0 increases, the effect size d increases (σ = 5 does not change). \
\
From the plot above, we can see that as the effect size gets larger, the power, which is represented as the yellow proportion, gets larger.


```{r}
output_result %>%
  group_by(true_mu) %>% 
  summarize(avg_estimate_mu = sum(estimate)/n()) %>% 
  mutate(
    true_mu = str_c("true mu = ",true_mu)
  ) %>% 
  ggplot(aes(x = true_mu, y = avg_estimate_mu, fill = true_mu))+
  geom_point(size=3,alpha=0.7,color = "tomato2")+
  labs(title = "all samples",x="true mu",y="average estimated mu")+
  geom_text(aes(label=round(avg_estimate_mu,2)),hjust=0, vjust=-1)+
  theme(text = element_text(size=20))
 
output_result %>%
  filter(p.value<0.05) %>%
  group_by(true_mu) %>% 
  summarize(avg_estimate_mu = sum(estimate)/n()) %>%
  mutate(
    true_mu = str_c("true mu = ",true_mu)
  ) %>% 
  ggplot(aes(x = true_mu, y = avg_estimate_mu, fill = true_mu))+
  geom_point(size=3,alpha=0.7,color = "blue")+
  labs(title = "only include samples for which the null was rejected",x="true mu",y="average estimated mu")+
  geom_text(aes(label=round(avg_estimate_mu,2)),hjust=0, vjust=-1)+
  theme(text = element_text(size=20))
```
\
The sample average of μ̂  across tests for which the null is rejected approximately equal to the true value of μ.\
As the true μ departs from 0, the average of μ̂ becomes closer and closer to the true μ. This is because as the true μ departs from 0, the proportion of samples that reject H0 gets larger (effect size increases, the power of the test increases). Thus, the average of the samples that reject H0 becomes closer to the true μ.



