---
title: "P8105 Homework5"
author: "Xiangyi Liu (xl3048)"
date: "11/10/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data.

```{r, warning=FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r p2_df}
path_df = 
  tibble(
    path = list.files("./data/data"),
  ) %>%
  mutate(
    path = str_c("./data/data/",path),
    data = map(.x=path, ~ read.csv(.x)),
    file = list.files("./data/data")
  ) %>%
  select(-path) %>%
  relocate(file,data) %>%
  unnest(data) %>%
  separate(file,sep = "_", into = c("arm","ID")) %>%
  mutate(
    arm = case_when(
      arm == "con" ~ "control",
      arm == "exp" ~ "experimental"
    )
  ) %>%
  unite(arm_id,arm,ID,sep = "_")
path_df$arm_id<-gsub("\\..*","",path_df$arm_id)

write.csv(path_df,file = "./data/prob2_path_df.csv")

head(path_df)
```


```{r p2_plot}
path_longer_df<-path_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>%
  separate(arm_id,sep = "_",into = c("arm","id")) %>%
  unite(arm_id,arm,id,sep = "_",remove = F) %>%
  select(-id)


p<-ggplot(data = path_longer_df, aes(x = week, y = value, group = arm_id, color = arm))+
  geom_line()
p
```

At Week 1, two groups did not appear a significant difference. Only two participants from the experimental group had noteworthy higher measurements compared to the control group.\
During the course of the study, the difference between the two groups became gradually obvious. The measurements taken from the control group roughly remained at the same level from Week 1 to Week 8. However, the measurements taken from the experimental group increased steadily every week. At Week 8, all participants in the experimental group had a higher measurements than that of the control group. 

## Problem 3
```{r cache=TRUE}
set.seed(1)

sim_mean_sd = function(samp_size=30, mu, sigma = 5) {

  sim_data = list(
    x=rnorm(n=samp_size, mean = mu, sd = sigma)
  ) %>% bind_rows()
  
}

sim_data <- rerun(5,sim_mean_sd(mu=0))


result <- tibble(
  t_test = map(.x=sim_data,~t.test(.x))
 ) %>%
  mutate(
   tidy_tests = map(.x = t_test, ~broom::tidy(.x))
 ) %>%
select(-t_test) %>%
unnest(tidy_tests) %>%
select(estimate,p.value) %>%
rename(mu_hat = estimate)

head(result) %>% knitr::kable(digits = 3)

  
```


```{r cache=TRUE}
mu_list = 
  list(
    "mu_1"  = 1, 
    "mu_2"  = 2, 
    "mu_3" = 3, 
    "mu_4" = 4,
    "mu_5" = 5,
    "mu_6" = 6)

trial_num = 1000

output_data = 
  tibble(mu_list = c(1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = mu_list, ~rerun(trial_num, sim_mean_sd(mu = .x)))
  ) %>%
  unnest(output_lists)

output_result<-tibble(
  t_test = map2(.x=output_data$output_lists,.y = output_data$mu_list, ~t.test(.x,mu = .y))
) %>%
  mutate(
   tidy_tests = map(.x = t_test, ~broom::tidy(.x))
 )%>%
select(-t_test) %>%
unnest(tidy_tests) %>%
cbind(output_data$mu_list) %>%
rename(true_mu = `output_data$mu_list`) %>%
select(true_mu, estimate,p.value) %>%
relocate(true_mu, estimate,p.value)
```

```{r p3_plot}
reject_null_prop <- output_result %>%
  group_by(true_mu) %>%
  summarize(
    reject_null = sum(p.value<0.05)/n()
  ) %>%
  mutate(true_mu=as.factor(true_mu),
         fail_reject_null = 1-reject_null) 

plot_reject_null_prop <-reject_null_prop %>%
  pivot_longer(
    reject_null:fail_reject_null,
    names_to = "condition",
    values_to = "proportion"
  )

p1<-ggplot(data = plot_reject_null_prop, aes(fill = condition, y = proportion, x = true_mu))+
  geom_bar(position="stack", stat="identity")+labs(title = "Proportion of Times Reject The Null")
p1

reject_null_prop%>% knitr::kable(digits = 3)
```




